%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

\usepackage{hyperref}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Adrien Tremblay}
\address{\href{https://www.adrientremblay.com/}{adrientremblay.com} \linebreak \href{https://www.linkedin.com/in/adrientremblay}{linkedin.com/in/adrientremblay/}}
\contacts{(514) 709-1678 \linebreak \href{mailto:adrientremblay.com}{adrien@adrientremblay.com}}

\begin{document}

	\makeheader

	\begin{cvsection}{Games}
		\begin{cvsubsection}{Completed}{}{}	
			\begin{itemize}
                \item \textbf{\href{https://adrientremblay.itch.io/dark-altar-2}{Dark Altar 2}} A first person horror game about collecting skulls to banish a possesed 
				monk. Implemented features: dynamic loading and unloading of models for optimized performance, advanced monster AI with varying levels of 
				aggression, spacial ambient audio for the forest environment. Made in Godot Game Engine.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Abandoned}{}{}	
			\begin{itemize}
                \item \textbf{\href{https://github.com/adrientremblay/bloodstone}{Bloodstone}} A lowpoly vampire FPS game where the player shoots and 
				uses various vampiric abilities to overthrow an oppressive regime of vampire hunters. Implemented features: modular levels, modeled and rigged hand and gun 
				with shooting and reloading animations, particle effects for vampire teleportation. Made in Godot Game Engine.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Game Jams}
		\begin{cvsubsection}{Solo}{}{}	
			\begin{itemize}
                \item \textbf{\href{https://ldjam.com/events/ludum-dare/58/gravelight}{Ludum Dare 58 - Gravelight (SOLO)}}A lowpoly first person simulation horror game about digging up graves to collect various artifacts while evading the groundskeepers. Godot Game Engine.
                \item \textbf{\href{https://ldjam.com/events/ludum-dare/55/dark-altar}{Ludum Dare 55 - Dark Altar (SOLO)}} Puzzle game based on placing "offerings" on a 5x5 grid such that the row/column sums equal the desired numbers in order to summon demons. Godot Game Engine.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Group}{}{}	
			\begin{itemize}
                \item \textbf{\href{https://github.com/Aoof/MyHouseIsBuiltForYou}{GAMERella 2025 - My House Is Build For You (GROUP)}} A retro PSX style first-person walking simulator game where you play as a housewife trapped in a toxic marriage and must choose how to interact with objects to complete tasks. Entry in GAMERella Jam 2025 (completed in a group) Unity Game Engine, Blender.
                \item \textbf{\href{https://github.com/Chavero2001/MDG_Game}{MDG Jam 2025 - Newcomer (GROUP)}} A topdown bullethell game where you play as an alien invading earth. The player can melee attack humans to absorb their stats and thrown projectile type. Entry in the MDG Game Jam 2025 (completed in a group) Unity Game Engine, Blender.
                \item \textbf{\href{https://ldjam.com/events/ludum-dare/53/snail-mail-2}{Ludum Dare 53 - Snail Mail (GROUP)}} Graph theory puzzle game about pathing coloured mail delivery snails to delivery mail while avoiding slime of their own colour. C++, SFML.
				\item \textbf{\href{https://ldjam.com/events/ludum-dare/52/galactic-garden}{Ludum Dare 52 - Galactic Garden (GROUP)}} Top down space shooter about planting space crops and defending them from invading cosmic crows. C++, SFML.
				\item \textbf{\href{https://ldjam.com/events/ludum-dare/51/forest-of-the-lost}{Ludum Dare 51 - Forest of the Lost (GROUP)}} Story and horror game about uncovering the dark secrets of a forest where children go missing. C++, SFML.
				\item \textbf{\href{https://ldjam.com/events/ludum-dare/50/final-forest}{Ludum Dare 50 - Final Forest (GROUP)}} Real Time Strategy game about defending a forest from invading lumberjacks by deploying various woodland creatures. C++, SFML.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Projects}
		\begin{cvsubsection}{Websites}{}{}
			\begin{itemize}
                \item \textbf{\href{https://github.com/adrientremblay/jai-soif-montreal}{jaisoifmontreal.com}} A website where all public water fountains in Montreal are visualized on an interactive map. Users can also click on individual fountains to see further details. PostgreSQL, Java Spring, Angular.
                \item \textbf{\href{https://github.com/adrientremblay/first-person-site}{adrientremblay.com}} A first person lowpoly 3D personal website where users can look around and interact with a virtual computer to access my real personal portfolio website. Three.js, Jekyll, Blender, Nginx.
			\end{itemize}
		\end{cvsubsection}
		
		\newpage

		\begin{cvsubsection}{Graphics}{}{}
			\begin{itemize}
                \item \textbf{\href{https://github.com/adrientremblay/RayTracer}{Ray Tracer}} A program that renders scene data encoded as a JSON. Features gamma correction, point and area lights. Eigen3. C++.
                \item \textbf{\href{https://github.com/adrientremblay/AudioVisualizer}{Open GL Audio Visualizer}} An interactive OpenGL application that performs a Fourmier transform on music being played and displays the audio spectrum by rendering 3D bars of varying heights or applying these values to vertex normals on a given model.OpenGl. C++.
                \item \textbf{\href{https://github.com/adrientremblay/RayCaster}{Ray Caster}} A simple textured ray casting render (DOOM inspired 2.5D rendering technique) where the player can walk around a small area. OpenGL. C++.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Open Source Contributions}
		\begin{cvsubsection}{\href{https://github.com/raycastly/texture-ripper}{Texture Ripper}}{}{}
			A JavaScript Electron app to extract textures from images using homography.
			\begin{itemize}
				\item Changed default scaling of textures to keep aspect ratio
				\item Ability to delete textures via keyboard
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{\href{https://github.com/konvajs/site}{Konva JS}}{}{}
			A Javascript 2D canvas framework for web and electron apps.
			\begin{itemize}
				\item Fixed typos in Node API page
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Software Developer}{GURUS Solutions}{June 2023 - Present}
			\begin{itemize}
                \item Solutioned then implemented NetSuite customizations for clients using the Javascript SuiteScript API.
                \item Developed integrations between different systems using the Boomi Integration Platform.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Engineer, Intern}{Matrox Video}{May 2022 - September 2022}
		    Display Wall Low Level	
			\begin{itemize}
                \item Collaborated with senior developers to enhance C++ code and resolve existing bugs.
                \item Worked on a in-house tool to test video functionality.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Engineer, Intern}{Genetec}{September 2021 - December 2021}	
            Core Platform
			\begin{itemize}
                \item Contributed to a new pipeline architecture project in C\# and the .NET framework.
                \item Resolved various existing bugs on the company flagship product: Security Center.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Tester, Intern}{Nakisa}{May 2021 - September 2021}		
			\begin{itemize}
                \item Developed automated integration tests using Selenium.
                \item Wrote and improved existing unit tests using JUnit.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Montreal, Canada}{Concordia University}{Winter 2018 - Winter 2023}
			\begin{itemize}
				\item B.S.E. in Software Engineering.
                \item Coursework: Operating Systems; Databases; Data Structures \& Algorithms; Computer Graphics; Programming Languages; System Hardware; Discrete Mathematics; Compilers.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

\end{document}

