%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

\usepackage{hyperref}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Adrien Tremblay}
\address{\href{https://www.adrientremblay.com/}{adrientremblay.com} \linebreak \href{https://github.com/adrientremblay}{github.com/adrientremblay}}
\contacts{(514) 709-1678 \linebreak \href{mailto:adrientremblay.com}{adrien@adrientremblay.com}}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Software Developer}{GURUS Solutions}{June 2023 - Present}
			\begin{itemize}
                \item Solutioned then implemented NetSuite customizations for clients using the Javascript SuiteScript API.
                \item Developed integrations between different systems using the Boomi Integration Platform.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Engineer, Intern}{Matrox Video}{May 2022 - September 2022}
		    Display Wall Low Level	
			\begin{itemize}
                \item Collaborated with senior developers to enhance C++ code and resolve existing bugs.
                \item Worked on a in-house tool to test video functionality.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Engineer, Intern}{Genetec}{September 2021 - December 2021}	
            Core Platform
			\begin{itemize}
                \item Contributed to a new pipeline architecture project in C\# and the .NET framework.
                \item Resolved various existing bugs on the company flagship product: Security Center.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Tester, Intern}{Nakisa}{May 2021 - September 2021}		
			\begin{itemize}
                \item Developed automated integration tests using Selenium.
                \item Wrote and improved existing unit tets using JUnit.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Montreal, Canada}{Concordia University}{Winter 2018 -- Winter 2023}
			\begin{itemize}
				\item B.S.E. in Software Engineering.
                \item Coursework: Operating Systems; Databases; Data Structures \& Algorithms; Computer Graphics; Programming Languages; System Hardware; Discrete Mathematics; Compilers.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Personal Projects}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{\href{https://github.com/adrientremblay/RayTracer}{Ray Tracer}} (2023). Program that ray traces an image given a JSON file describing the geometry of a scene and the intended render parameters. Capable of global illumination ray tracing and local illumination path tracing. C++, JSON 
                \item \textbf{\href{https://github.com/adrientremblay/AudioVisualizer}{Audio Frequency Visualizer}} (2023). Interactive visual program that plays an audio file, performs signal processing on the stream, and visualizes the audio frequencies either as 2D bars, 3D bars, or a 3D mesh. Features UI elements to configure the render. C++, OpenGL 
                \item \textbf{\href{https://github.com/adrientremblay/Compiler}{Compiler}} (2023). Table-Driven Top-Down Compiler for a C++ like language. Java
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Game Jams and Hackathons}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
                \item \textbf{\href{https://ldjam.com/events/ludum-dare/53/snail-mail-2}{Ludum Dare 53 - Snail Mail (Summer 2023)}} Graph theory puzzle game about pathing coloured mail delivery snails to delivery mail while avoiding slime of their own colour. C++, SFML.
				\item \textbf{\href{https://ldjam.com/events/ludum-dare/52/galactic-garden}{Ludum Dare 52 - Galactic Garden (Winter 2023)}} Top down space shooter about planting space crops and defending them from invading cosmic crows. C++, SFML.
				\item \textbf{\href{https://ldjam.com/events/ludum-dare/51/forest-of-the-lost}{Ludum Dare 51 - Forest of the Lost (Fall 2022)}} Story and horror game about uncovering the dark secrets of a forest where children go missing. C++, SFML.
				\item \textbf{\href{https://ldjam.com/events/ludum-dare/50/final-forest}{Ludum Dare 50 - Final Forest (Summer 2022)}} Real Time Strategy game about defending a forest from invading lumberjacks by deploying various woodland creatures. C++, SFML.
				\item \textbf{\href{https://github.com/Team-Blockchain-Ai-Machine-Learning/Spotifeels}{ConU Hacks V - Spotifeels (Summer 2022)}} Hackathon Django and React.js web app to regularlly query employees on mental wellness. Javascript, Python, Django, React.js.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}

