%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

\usepackage{hyperref}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Adrien Tremblay}
\address{\href{https://www.adrientremblay.com/}{adrientremblay.com} \linebreak \href{https://www.linkedin.com/in/adrientremblay}{linkedin.com/in/adrientremblay/}}
\contacts{(514) 709-1678 \linebreak \href{mailto:adrientremblay.com}{adrien@adrientremblay.com}}

\begin{document}

	\makeheader

	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Software Developer}{GURUS Solutions}{June 2023 - Present}
			\begin{itemize}
                \item Solutioned then implemented NetSuite customizations for clients using the Javascript SuiteScript API.
                \item Developed integrations between different systems using the Boomi Integration Platform.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Engineer, Intern}{Matrox Video}{May 2022 - September 2022}
		    Display Wall Low Level	
			\begin{itemize}
                \item Collaborated with senior developers to enhance C++ code and resolve existing bugs.
                \item Worked on a in-house tool to test video functionality.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Engineer, Intern}{Genetec}{September 2021 - December 2021}	
            Core Platform
			\begin{itemize}
                \item Contributed to a new pipeline architecture project in C\# and the .NET framework.
                \item Resolved various existing bugs on the company flagship product: Security Center.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Tester, Intern}{Nakisa}{May 2021 - September 2021}		
			\begin{itemize}
                \item Developed automated integration tests using Selenium.
                \item Wrote and improved existing unit tests using JUnit.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Projects}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
                \item \textbf{\href{https://github.com/adrientremblay/AudioVisualizer}{Open GL Audio Visualizer}} An interactive OpenGL application that performs a Fourmier transform on music being played and displays the audio spectrum by displaying bars of varying heights and applying these values to vertex normals on a model.OpenGl. C++.
                \item \textbf{\href{https://github.com/adrientremblay/RayTracer}{Ray Tracer}} A program that renders scene data encoded as a JSON. Features gamma correction, point and area lights. Eigen3. C++.
                \item \textbf{\href{https://github.com/adrientremblay/RayCaster}{Ray Caster}} A simple ray casting (DOOM and Wolfenstein 2.5D rendering technique) renderer where the player can walk around a small area. OpenGL. C++.
                \item \textbf{\href{https://ldjam.com/events/ludum-dare/58/gravelight}{Gravelight}} A lowpoly first person simulation horror game about digging up graves to collect various artifacts while evading the groundskeepers. Godot Game Engine.
                \item \textbf{\href{https://github.com/adrientremblay/dark-altar-2}{Dark Altar 2}} A first person horror game about collecting skulls to banish a possesed monk. Godot Game Engine.
                \item \textbf{\href{https://github.com/adrientremblay/bloodstone}{Bloodstone)}} A lowpoly vampire FPS game where the player shoots and uses various vampiric abilities to overthrow an oppressive regime of vampire hunters. Godot Game Engine.
                \item \textbf{\href{https://ldjam.com/events/ludum-dare/55/dark-altar}{Dark Altar}} Puzzle game based on placing "offerings" on a 5x5 grid such that the row/column sums equal the desired numbers in order to summon demons. Godot Game Engine.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Montreal, Canada}{Concordia University}{Winter 2018 - Winter 2023}
			\begin{itemize}
				\item B.S.E. in Software Engineering.
                \item Coursework: Operating Systems; Databases; Data Structures \& Algorithms; Computer Graphics; Programming Languages; System Hardware; Discrete Mathematics; Compilers.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Skillset}
			\begin{cvsubsection}{}{}{}	
				\begin{itemize}
					\item \textbf{Languages:} C, C++, Python, Java, Javascript, Typescript, Kotlin, Rust, C\#, GDscript, Swift, Go, PHP, Ruby, Bash, HTML, CSS.
					\item \textbf{Frameworks:} React, Angular, Vue.js, Django, Spring Boot, Three.js, Svelte, Next.js, jQuery, Bootstrap, Node.js, Express.js, Flask, Jekyll, ASP.NET Core, Ruby on Rails, Laravel.
					\item \textbf{Databases:} MySQL, PostgreSQL, MySQL, NoSQL, MongoDB, Redis.
					\item \textbf{Cloud Platforms:} Docker, Kubernetes, AWS (EC2, S3, Lambda, RDS), Azure, Jenkins, GitHubActions, Nginx, Apache.
					\item \textbf{Misc Technologies:} Git, Kafka, SQS, SNS, REST APIs, JIRA.
					\item \textbf{Game Engines:} Godot, Unity, Unreal Engine, SFML.
					\item \textbf{Data \& Analytics:} Pandas, NumPy, Matplotlib, TensorFlow, PyTorch, scikit-learn, Apache Spark, Hadoop.
					\item \textbf{Mobile Development:} React Native, Flutter.
					\item \textbf{Operating Systems:} Linux, Windows, macOS.
					\item \textbf{Software Engineering:} Agile, Waterflow, Kanban Boards, Design Patterns, Object-Oriented Programming, Test-Driven Development, MVC, CI.
				\end{itemize}
			\end{cvsubsection}
		\end{cvsection}

	
\end{document}

